Stuff related to tensor products of modal algebras

### 2020-06-23 filtration-stuff/Text.tex
update

By ${\bf K5}$ we mean the logic ${\bf K} \oplus {A5}$, where ${A5} = \Diamond p \to \Box \Diamond p$. It is known that ${\bf K5}$ is the modal logic of all Euqlidean frames. A frame is called Euqlidean if for each $x, y, z$ one has $x R y$ and $x R z$

@@

\begin{defin}
  Let $\mathcal{M} = \langle W, R_1, \dots, R_n, \vartheta \rangle$ be a Kripke model and $\Gamma$ be a Sub-closed set formulas. A $\Gamma$-filtration of $\mathcal{M}$ is a model
  $\widehat{\mathcal{M}} = \langle \widehat{W}, \widehat{R_1}, \dots, \widehat{R_n}, \widehat{\vartheta} \rangle$ such that:
  \begin{enumerate}
    \item $\widehat{W} = W / \sim$, where $\sim$ is an equivalence relation having a finite index that respects $\Gamma$
    \item $\widehat{\vartheta}(p) = \{ [x]_{\sim} \: | \: x \in W \: \& \: x \in \vartheta(p)\}$
    \item For each $i \in I$ one has $\widehat{R}_i^{\text{min}} \subseteq \widehat{R}_i \subseteq \widehat{R}_i^{\text{max}}$. $\widehat{R}_{i, \sim}^{\text{min}}$ is the $i$-th minimal filtered relation on $\widehat{W}$ defined as
    \begin{center}
      $\hat{x} \widehat{R}_{i, \sim}^{\text{min}} \hat{y} \Leftrightarrow \exists x' \sim x \: \exists y' \sim y \: x R_i y$
    \end{center}
    $\widehat{R}_{\Gamma,i}^{\text{max}}$ is the $i$-th maximal filtered relation on $\widehat{W}$ induced by $\Gamma$ defined as
    \begin{center}
      $\hat{x} \widehat{R}_{\Gamma,i}^{\text{max}} \hat{y} \Leftrightarrow \forall \Box_i \varphi \in \Gamma (\mathcal{M}, x \models \Box_i \varphi \Rightarrow \mathcal{M}, y \models \varphi)$
    \end{center}
  \end{enumerate}
\end{defin}

If $\Phi$ is finite subset of $\Gamma$ and $\sim = \sim_{\Gamma}$, then $\widehat{M}$ is a definable $\Gamma$-filtration of $\mathcal{M}$ through $\Phi$.

@@

\section{Filtration of Euclidian logics}

>>>>

By ${\bf K5}$ we mean the logic ${\bf K} \oplus {A5}$, where ${A5} = \Diamond p \to \Box \Diamond p$. It is known that ${\bf K5}$ is the modal logic of all Euclidean frames. A frame is called Euclidean if for each $x, y, z$, $x R y$ and $x R z$ implies $y R z$.

\begin{prop}
  Let $\mathcal{F} = \langle W, R \rangle$ be an Euclidean frame.

  \begin{enumerate}
    \item For each $x, y, z \in W$, $x R y$ and $x R z$ implies either $y R z$ or $z R y$.
    \item $R \subseteq R ; R$, that is, $R$ is dense.
    \item For each $x \in W$, $R^{*}(x) = \{ x\} \cup R(R(x))$.
  \end{enumerate}
\end{prop}

@@

\begin{defin}
  Let $\mathcal{M} = \langle W, R_1, \dots, R_n, \vartheta \rangle$ be a Kripke model and $\Gamma$ be a Sub-closed set formulas. A $\Gamma$-filtration of $\mathcal{M}$ is a model
  $\widehat{\mathcal{M}} = \langle \widehat{W}, \widehat{R_1}, \dots, \widehat{R_n}, \widehat{\vartheta} \rangle$ such that:
  \begin{enumerate}
    \item $\widehat{W} = W / \sim$, where $\sim$ is an equivalence relation having a finite index that respects $\Gamma$
    \item $\widehat{\vartheta}(p) = \{ [x]_{\sim} \: | \: x \in W \: \& \: x \in \vartheta(p)\}$
    \item For each $i \in I$ one has $\widehat{R}_i^{\text{min}} \subseteq \widehat{R}_i \subseteq \widehat{R}_i^{\text{max}}$. $\widehat{R}_{i, \sim}^{\text{min}}$ is the $i$-th minimal filtered relation on $\widehat{W}$ defined as
    \begin{center}
      $\hat{x} \widehat{R}_{i, \sim}^{\text{min}} \hat{y} \Leftrightarrow \exists x' \sim x \: \exists y' \sim y \: x R_i y$
    \end{center}
    $\widehat{R}_{\Gamma,i}^{\text{max}}$ is the $i$-th maximal filtered relation on $\widehat{W}$ induced by $\Gamma$ defined as
    \begin{center}
      $\hat{x} \widehat{R}_{\Gamma,i}^{\text{max}} \hat{y} \Leftrightarrow \forall \Box_i \varphi \in \Gamma \: (\mathcal{M}, x \models \Box_i \varphi \Rightarrow \mathcal{M}, y \models \varphi)$
    \end{center}
  \end{enumerate}
\end{defin}

If $\Phi$ is finite subset of $\Gamma$ and $\sim = \sim_{\Phi}$, then $\widehat{M}$ is a definable $\Gamma$-filtration of $\mathcal{M}$ through $\Phi$. If $\sim = \sim_{\Gamma}$, then such a filtration by means of the definiton above is called \emph{strict}.

@@

\begin{defin} Let $\mathbb{F}$ be a class of Kripke frames and $\Gamma$ a finite set of formulas closed under subformulas. If for every model $\mathcal{M}$ over $\mathcal{F} \in \mathbb{F}$ there exists a model that is a $\Gamma$-definable filtration of $\mathcal{M}$, then $\mathbb{F}$ admits definable filtration. A class of models $\mathbb{M}$ admits definable filtration if for every $\mathcal{M} \in \mathbb{M}$ there exists a model belonging to the same class that is a definable $\Gamma$-filtration of $\mathcal{M}$.
\end{defin}

\begin{lemma}
  $ $

\begin{enumerate}
  \item Let $\mathcal{L}$ be a complete normal modal logic. If $\operatorname{Frames}(\mathcal{L})$ admits filtration, then $\mathcal{L}$ has the finite model property.
  \item If the class of models $\operatorname{Mod}(\mathcal{L})$ admits filtration, then $\mathcal{L}$ has the finite model property and Kripke complete as well.
\end{enumerate}
\end{lemma}

\section{Filtration of Euclidean logics}

First of all, let us ensure that a filtration of an Euclidean frame is not necessary finite.
Let $[x] \sim_{\Gamma} [y]$ and $[x] \sim_{\Gamma} [z]$. Then for some $x' \in [x]$ $y' \in [y]$, one has
$x' R y'$ and $x'' R z'$ for some $x'' \in [x]$ and $z' \in [z]$. Clearly, we cannot claim that $x' = x''$ in general. Thus, minimal filtration does not preserve the required property.

### 2020-06-23 tensor-product-stuff/Text.tex
update

\begin{defin} Let $\mathcal{F}_1 = \langle W_1, R_1^1, \dots, R_1^n\rangle$ be an $n$-frame and $\mathcal{F}_2 = \langle W_2, R_2^1, \dots, R_2^m\rangle$.
The product frame of $\mathcal{F}_1$ and $\mathcal{F}_2$ is an $n+m$-frame of the form
\begin{center}
$\mathcal{F}_1 \times \mathcal{F}_2 = \langle W_1 \times W_2, R_h^1, \dots, R_h^n, R_v^1, \dots, R_v^m \rangle$
\end{center}
such that for all $u_1, u_2 \in W_1$ and for all $v_1, v_2 \in W_2$,
\begin{center}
  $\langle u_1, v_1 \rangle R^i_h \langle u_2, v_2 \rangle$ iff $u_1 R_1^i u_2$ and $v_1 = v_2$ for
  $1 \leq i \leq n$.

  $\langle u_1, v_1 \rangle R^j_v \langle u_2, v_2 \rangle$ iff $u_1 = u_2$ and $u_1 R_2^j u_2$ for $1 \leq j \leq m$.
\end{center}
\end{defin}

Let $\mathcal{L}_1$ be a normal $n$-modal logic and $\mathcal{L}_2$ a normal $m$-modal logic, the product of $\mathcal{L}_1$ and $\mathcal{L}_2$ is defined as

\begin{center}
  $\mathcal{L}_1 \times \mathcal{L}_2 = \operatorname{Log}(\operatorname{Frames}(\mathcal{L}_1 ) \times \operatorname{Frames}(\mathcal{L}_2))$
\end{center}

\begin{prop}
  $ $

  \begin{enumerate}
    \item Let $\mathcal{L}_1$, $\mathcal{L}_2$ be modal logics, then $\mathcal{L}_1 * \mathcal{L}_2 \subseteq \mathcal{L}_1 \times \mathcal{L}_2$.
    \item Let $\mathcal{L}_1$, $\mathcal{L}_2$ be Kripke complete modal logics, then $\mathcal{L}_1 \times \mathcal{L}_2 = \operatorname{Log}(\operatorname{Frames}_r(\mathcal{L}_1) \times \operatorname{Frames}_r(\mathcal{L}_2))$, where $\operatorname{Frames}_r(\mathcal{L}_i) = \{\mathcal{F} \in \operatorname{Frames}(\mathcal{L}_i) \: | \: \mathcal{F} \text{ is rooted }\}$ for $i = 1,2$.
  \end{enumerate}
\end{prop}

\subsection{Axiomatising products}

The following properties hold for a product frame having the form $\mathcal{F} = \langle W, R_1, \dots, R_n \rangle$:

\begin{enumerate}
  \item commutativity 1
  \item commutativity 2
  \item confluence
\end{enumerate}

@@

>>>>

\begin{defin} Let $\mathcal{F}_1 = \langle W_1, R^1_1, \dots, R^1_n\rangle$ be an $n$-frame and $\mathcal{F}_2 = \langle W_2, R^2_1, \dots, R^2_m\rangle$ an $m$-frame
\end{defin}

\begin{defin} discrete duality between perfect modal algebras and Kripke frames
\end{defin}

@@

\newpage
